---
title: 'Project 5: Blending and Visualizations with R and Tableau'
output: html_document
--- 

#### This html page, produced by creating an R markdown document, and using KnitR to knit the file into html. The purpose of this html file, is to show our analysis of our data set in Tableau and R Studio. The data set is test car information including, horse power, emissions, engine size, and safety ratings . This data was blended with a second data set that has additional information about 2016 cars. This html also shows the steps required to reproduce our findings, given the same data. Given the variables in our data set, we were able to query the data base in a few different ways and use Tableau to create visualizations to better analyze the data. The tableau graphs, are then saved as images and inserted into this html through the .rmd file.

##### Rprofile.R:
An Rprofile.R document was created to include all of the packages required for the project, in order to avoid requiring packages in each of the R script files. Below is the call to the Rprofile document, and shows the necessary packages being loaded:


```{r}
source("../Rprofile.R", echo = FALSE)
```



#### Project 4 Scatter Plot (R):
Below is our first visualization of a subset of the data. The graph is a scatter plot showing horse power on the x-axis and CO2 emissions on the y-axis. As expected there is a positive correlation between the two measure variables. The visualization shows a trend of increased carbon dioxide emissions with increases in horesepower. The colors represent different vehicle types. This is similar to the visualization made for the previous project in Tableay, but made in R studio.

```{r}
source("../03 R SQL Visualizations/scatter.R", echo = TRUE)
```

#### Project 4 Bar Chart (R):
Below is a visualization of a subset of the data. We thought it would be insightful to see how the variables changed over the time period between 2000 and 2012. As The faceted graph shows, there is a trickling of data points, representing countries, from the lower end of the graph to the upper end of the graph showing that literacy rates were improving through the years. It was surprising however to see that percentage of GDP spent on education seemed to play little role in the improvement of youth literacy rates over the years. This is similar to the visualization made for the previous project in Tableay, but made in R studio.

# ```{r}
# source("../03 R SQL Visualizations/bar-chart.R", echo = TRUE)
# ```

#### Project 4 Cross-Tab (R):
Below is another visualization of a subset of the data. For this visualization, we wanted to observe a cross tab of vehicle types, car makes, and the calculated engine efficiency of the vehicles. Engine efficiency was calculated by dividing the horsepower by the engine displacement, or size of the engine in Liters. Parameters were set for high and low engine efficiency and used to compare all of the vehicles in the cross-tab. This is similar to the visualization made for the previous project in Tableay, but made in R studio.

```{r}
source("../03 R SQL Visualizations/cross-tab.R", echo = TRUE)
```


#### Tableau Blend Visualization :
The below visualization was done by blending our two data sets, since both data sets have similarites such as vehicle manufacturer, the two sets were easily blended and produced some expected results when we compared rated horsepower of cars from one data set, to the fuel efficiency in the other data set. As the visualization shows, the relationship is inverse; the greater the horsepower, the lower the fuel efficiency.


#### R Studio Blend Visualization :
This is a reproduction of the above Visualization done Using R studio to blend and visualize the data.

```{r}
source("../03 R SQL Visualizations/blended.R", echo = TRUE)
```


